### 2022-06-03 main/paper2.tex
Add files via upload

A simple way to represent the DIG $G$ of a dynamical system is via the adjacency matrix $\textbf{DIG}=[d_{i,j}]_{m\times m}$ that is defined by
\begin{align}
    d_{j,i} = \left\{
\begin{array}{ll}
      1 & \text{if}\  I(R_i\rightarrow R_j||\mathcal{R}_{-\{i,j\}})>0,\\
      0 & \text{otherwise}. \\
\end{array} 
\right. 
\end{align}
Given a DIG $G=(\mathcal{V},\mathcal{E})$, we define the parent set of node $R_j$ denoted by $\mathcal{PA}_j\subset \mathcal{V}$ to be the set of all times series that have direct influences on $R_j$, i.e., $\mathcal{PA}_j:=\{R_k: d_{j,k}=1\}$. Similarly, the children set of node $R_j$ is given by $\mathcal{CH}_j:=\{R_k: d_{k,j}=1\}$. 
Next example demonstrates the DIG of a simple linear system.
\begin{example}\label{r1}
Consider a network of three times series $\{X,Y,Z\}$ with the following linear dynamic,
\begin{small}
\begin{equation}\label{model1}
\begin{pmatrix}
X_t \\
Y_t\\
Z_t
\end{pmatrix}=\begin{pmatrix}
0.5 & 0& 0\\
0.4 & 0.5 & 0\\
0 & -0.2 & 0
\end{pmatrix}\begin{pmatrix}
X_{t-1} \\
Y_{t-1}\\
Z_{t-1}
\end{pmatrix}+\begin{pmatrix}
N_{X_t} \\
N_{Y_t}\\
N_{Z_t}
\end{pmatrix},
\end{equation}
\end{small}
where $N_X$, $N_Y$, and $N_Z$ are three independent stationary Gaussian processes with zero mean and a diagonal covariance matrix (1, 0.9, 1). 
Since the dynamic is linear and the exogenous noises are Gaussian, we can compute the DIs using the following expression\footnote{Equation \eqref{simueq} does not hold in general setting.}\citet{acc2014}.
\begin{equation}\label{simueq}
I(Z\rightarrow Y||X)=\frac{1}{2T}\sum_{t=1}^{T}\log\frac{|\Sigma_{Y_{t-1},Y_{t},X_{t-1}}||\Sigma_{Z_{t-1},Y_{t-1},X_{t-1}}|}{|\Sigma_{Y_{t-1},X_{t-1}}||\Sigma_{Z_{t-1},Y_{t-1},Y_{t},X_{t-1}}|},
\end{equation}
where $|\Sigma_{Y_{t-1},Y_{t},X_{t-1}}|$ denotes the determinant of the covariance matrix of $\{Y_{t-1},Y_{t},X_{t-1}\}$. Using \eqref{simueq}, we computed the DIs of this system,
\begin{figure}
\hspace{4cm}
\xygraph{ !{<0cm,0cm>;<1.9cm,0cm>:<0cm,1.7cm>::} 
!{(-.7,1) }*+{X}="x"
!{(.4,1.6) }*+{Y}="y"
!{(1.5,1)}*+{Z}="z"
%"x":@(ld,lu)"x"
%"y":@(lu,ru)"y"
"x":"y"
"y":"z"
}
   \caption{DIG of the system in \eqref{model1}.}\label{fig:example_dig}
\end{figure}
\begin{small}
\begin{align*}
&I(Y\rightarrow X||Z)=0,\ \ I(Z\rightarrow X||Y)=0,\ \ I(Z\rightarrow Y||X)=0,\ \ I(Z\rightarrow Z||X,Y)=0,\\
&I(X\rightarrow Z||Y)=0,\ \ \ \ I(X\rightarrow Y||Z)\approx 0.1, \ \ \ I(Y\rightarrow Z||X)\approx 0.03.
\end{align*}
\end{small}
Figure \ref{fig:example_dig} illustrates the DIG of this system. In this example, $\mathcal{PA}_Z=\{Y\}$ and $\mathcal{CH}_Z=\{\}$.
\end{example}

@@

In this setting, the results of Lemma \ref{lemma:nonlinear} implies that the following time series can be substituted in the conditioning of the DI. 
\begin{align}
    Q_t = \sum_{k=1}^K w_{j,k} h_k(\mathcal{X}_{-\{i\},t-1}).
\end{align}
However, in this formulation, the weights $\{w_{,k}\}$ are unknown. 
An approach to obtain the weights is a non-linear filtering technique known as Koopman-based lifting \citet{koopman1931hamiltonian}. 
This technique takes observational data and a set of library functions as inputs and obtains the unknown coefficients $\{w_{,k}\}$.
The main steps of this technique are; transforming the data (lifting the data),  applying a linear identification on the lifted data, and finally applying another transformation to bring down the results into the original vector field.  Figure \ref{fig:koopman} illustrates the main steps. For more details see Appendix and \citet{mauroy2019koopman}. 
\begin{figure}
\centering
\includegraphics[scale=.4]{koopman.pdf}
\caption{Koopman lifting technique compared to classical non-linear identification.}\label{fig:koopman}
\end{figure}

@@

 \begin{algorithm}[t]
 \textbf{Input:} Observational data of $m$ time series up to time $T$, $\mathcal{X}^T$, Threshold $\alpha>0$\;
 \textbf{Output:} Adjacency matrix of $\textbf{DIG}=[d_{i,j}]$\;
 \For{ $i,j=1,...,m$}{
  Train an RNN $R_j(\cdot;\Theta^*)$ that maps $\mathcal{X}_{-\{i\}}^{t-1}$ to $X_{j,t}$\; 
  Define $Q_{t-1}=R_{j}(\mathcal{X}_{-\{i\}}^{t-1};\Theta^*)$\;
  \eIf{$I(X_{i}\rightarrow X_j || Q) > \alpha$}{
   $d_{j,i}=1$
   }{
   $d_{j,i}=0$
  }
  }
 \caption{Infer-DIG}\label{alg}
\end{algorithm}
 Given the aforementioned result, we train an RNN using the observational data to estimate the time series $Q$ defined in Lemma \ref{lemma:nonlinear}.
 More precisely, our RNN maps $\mathcal{X}_{-\{i\}}^{t-1}$ as the inputs to $X_{j,t}$ as the output. 
 Let $R_j(\mathcal{X}_{-\{i\}}^{t-1};\Theta^*)$ denotes the trained RNN with parameters $\Theta^*$. 
 In this case, the time series $Q$ can be written as  $Q_{t-1}=R_{j}(\mathcal{X}_{-\{i\}}^{t-1};\Theta^*)$.
 Finally, we use \eqref{eq:non-q} to detect whether $X_i$ has influence on $X_j$ or not. 
 Algorithm Infer-DIG in \ref{alg} summarizes the steps of our RNN method.

@@

To reflect an important property of the market that some firms are more connected than others in our experiment, we divided the $m$ time series into two parts. 
First part ($1\leq i\leq s$) indicates assets with high degrees of connectedness and the second part ($1+s\leq i\leq m$) are the ones with low degrees of connectedness.
Parameter $1<s<m$ denotes the numbers of assets with high degrees of connectedness.
Afterward, for every entry $(i,j)$ of $\textbf{A}$, we independently generated a random number $x\sim U(-0.9, 0.9)$ and decided on value $a_{i,j}$ as follows,
\begin{align}\label{eq:rules}
    a_{i,j}=\left\{
\begin{array}{ll}
      x 1_{|x| > \underline{\epsilon} },  & \text{if}\ \ 1\leq i\leq s, 1\leq j\leq s, \\
      x 1_{|x| > \overline{\epsilon} },  & \text{if}\ \ 1+s\leq i\leq m, 1\leq j\leq m, \\
      0,  & \text{if}\ \ 1\leq i\leq s, 1+s\leq j\leq m, \\
\end{array} 
\right.
\end{align}
where $1_{a>b}$ denotes the indicator function which is equal to 1 when $a>b$ and $0$ otherwise and $\underline{\epsilon}$ and $\bar{\epsilon}$ are thresholds to define non-zero entries in the upper-left and the lower part of $\textbf{A}$, respectively.
Figure \ref{fig:matrix} illustrates the structure of the resulting $\textbf{A}$.
We select these thresholds such that $\underline{\epsilon}<\bar{\epsilon}$. 
This ensures that the upper-left of $\textbf{A}$ is denser than its lower part or equivalently, assets with indices $\{1,...,s\}$ are more connected than the ones with indices $\{1+s,...,m\}$.
In our experiment, we select $(s,m)=(85,100)$ and $(\underline{\epsilon},\bar{\epsilon})=(0.4,0.7)$. 
%further results are robust to changes of parameters.
\begin{figure}
    \centering
    \includegraphics[scale=.2]{fig_matrix.pdf}
    \caption{Structure of matrix $\textbf{A}$ in \eqref{eq:ex_lin} that is build using \eqref{eq:rules}.}
    \label{fig:matrix}
\end{figure}
Finally, to guarantee the stability of the time series, we rescale\footnote{Formally, we use $\textbf{A}/(\rho(\textbf{A}) + \epsilon)$, where $0<\epsilon$.} $\textbf{A}$ such that its spectral radius is strictly less than one, i.e.,  $\rho(\textbf{A})< 1$. 
Once the matrix $\textbf{A}$ is defined, we simulate the time series using \eqref{eq:ex_lin} for a period of $T = 30000$ and use the resulting data for our estimations.

@@

\begin{figure*}
        \centering
        \begin{subfigure}[b]{0.48\textwidth}
            \centering
            \includegraphics[width=\textwidth]{Linear_Performance_True parents.jpg}
        \end{subfigure}
        \quad
        \begin{subfigure}[b]{0.48\textwidth}  
            \centering 
            \includegraphics[width=\textwidth]{Linear_Performance_Most correlated assets.jpg}
        \end{subfigure}
        \vskip\baselineskip
        \begin{subfigure}[b]{0.48\textwidth}   
            \centering 
            \includegraphics[width=\textwidth]{Linear_Performance_Ideal Portfolio.jpg}
        \end{subfigure}
                  \quad
        \begin{subfigure}[b]{0.48\textwidth}   
            \centering 
            \includegraphics[width=\textwidth]{Linear_Performance_RNN.jpg}
        \end{subfigure}
        \caption{Precision and recall curves in the linear framework for the \textit{True parents}, \textit{Most correlated}, \textit{Ideal portfolio}, and the \textit{RNN}, respectively.} 
        \label{perflin}
    \end{figure*}

@@

\begin{figure}
\centering
\includegraphics[width=\textwidth]{precrecall_15assets.jpg}
\caption{Precision-Recall curves for the quadratic model.}\label{fig:perfnonlin}
\end{figure}

@@

\end{tabular}
\caption{Degree of Granger Causality (DGC) for each sub-graph. DGC is defined as the fraction of relationships in the network among all potential relationships.}
\label{GrangerCausality}
\end{table}

\begin{figure*}
        \centering
        \begin{subfigure}[b]{0.6\textwidth}
            \centering
            \includegraphics[width=\textwidth]{net1994.JPG}
        \end{subfigure}
        \vskip\baselineskip
        \begin{subfigure}[b]{0.6\textwidth}   
            \centering 
            \includegraphics[width=\textwidth]{net1999.JPG}
        \end{subfigure}
        \caption{Empirical DIG for the periods 1990-1994 (top) and 1995-1999 (bottom). Interactive graphs can be found at https://marcaureledivernois.github.io/firm-network/} 
        \label{empdig1}
    \end{figure*}

\begin{figure*}[]
        \centering
        \begin{subfigure}[b]{0.6\textwidth}
            \centering
            \includegraphics[width=\textwidth]{net2004.JPG}
        \end{subfigure}
        \vskip\baselineskip
        \begin{subfigure}[b]{0.6\textwidth}   
            \centering 
            \includegraphics[width=\textwidth]{net2009.JPG}
        \end{subfigure}
        \caption{Empirical DIG for the periods 2000-2004 (top) and 2005-2009 (bottom). Interactive graphs can be found at https://marcaureledivernois.github.io/firm-network/} 
        \label{empdig2}
    \end{figure*}

\begin{figure*}
        \centering
        \begin{subfigure}[b]{0.6\textwidth}
            \centering
            \includegraphics[width=\textwidth]{net2014.JPG}
        \end{subfigure}
        \vskip\baselineskip
        \begin{subfigure}[b]{0.6\textwidth}   
            \centering 
            \includegraphics[width=\textwidth]{net2019.JPG}
        \end{subfigure}
        \caption{Empirical DIG for the periods 2010-2014 (top) and 2015-2019 (bottom). Interactive graphs can be found at https://marcaureledivernois.github.io/firm-network/} 
        \label{empdig3}
    \end{figure*}

\begin{table}[]
\resizebox{\textwidth}{!}{
\begin{tabular}{|ll|ll|ll|ll|ll|ll|}
\hline
\multicolumn{2}{|c|}{1990-1994} &
  \multicolumn{2}{c|}{1995-1999} &
  \multicolumn{2}{c|}{2000-2004} &
  \multicolumn{2}{c|}{2005-2009} &
  \multicolumn{2}{c|}{2010-2014} &
  \multicolumn{2}{c|}{2015-2019} \\ \hline
Ticker &
  Out &
  Ticker &
  Out &
  Ticker &
  Out &
  Ticker &
  Out &
  Ticker &
  Out &
  Ticker &
  Out \\ \hline
SBC  & 13 & JNJ  & 12 & XOM  & 12 & PEP  & 15 & SPY   & 17 & SPY   & 14 \\
CHV  & 11 & HWP  & 12 & JNJ  & 10 & WFC  & 13 & T     & 15 & DIS   & 12 \\
XON  & 10 & INTC & 12 & MSFT & 9  & CSCO & 12 & JNJ   & 15 & BRK   & 12 \\
PG   & 10 & BAC  & 12 & DELL & 9  & WMT  & 11 & CVX   & 13 & PFE   & 11 \\
GE   & 10 & PFE  & 11 & WMT  & 9  & IBM  & 11 & AAPL  & 12 & UNH   & 11 \\
AN   & 9  & IBM  & 11 & C    & 9  & PG   & 11 & INTC  & 12 & JPM   & 11 \\
BEL  & 9  & MSFT & 11 & HD   & 8  & CVX  & 11 & CSCO  & 12 & AAPL  & 10 \\
MRK  & 8  & SBC  & 11 & JPM  & 8  & HPQ  & 10 & GE    & 12 & GOOGL & 10 \\
IBM  & 8  & GE   & 10 & PFE  & 8  & VZ   & 10 & IBM   & 11 & WMT   & 9  \\
BMY  & 8  & MRK  & 10 & PG   & 7  & GE   & 9  & GOOGL & 11 & CSCO  & 9  \\
ABT  & 7  & LMG  & 9  & INTC & 7  & UBS  & 9  & XOM   & 11 & VZ    & 9  \\
AHP  & 7  & MO   & 9  & BAC  & 7  & PFE  & 9  & JPM   & 10 & BA    & 9  \\
T    & 7  & NT   & 9  & BMY  & 6  & C    & 9  & KO    & 10 & CVX   & 8  \\
BLS  & 7  & XOM  & 9  & SBC  & 6  & SLB  & 9  & MRK   & 10 & WFC   & 8  \\
AIG  & 7  & KO   & 9  & IBM  & 5  & MSFT & 9  & BRK   & 10 & V     & 8  \\
F    & 7  & HD   & 8  & TWX  & 5  & ORCL & 9  & SLB   & 10 & PG    & 8  \\
HWP  & 7  & BEL  & 8  & AIG  & 5  & MRK  & 8  & WMT   & 10 & T     & 7  \\
MOT  & 7  & BMY  & 8  & CSCO & 4  & KO   & 8  & VZ    & 9  & JNJ   & 7  \\
DD   & 6  & SUNW & 8  & GE   & 4  & GOOG & 7  & DIS   & 9  & MRK   & 7  \\
DIS  & 6  & AIG  & 7  & VZ   & 4  & XOM  & 7  & PFE   & 9  & KO    & 6  \\
MOB  & 6  & WCOM & 7  & MRK  & 4  & JNJ  & 7  & BAC   & 8  & XOM   & 5  \\
PEP  & 6  & CSCO & 6  & MOT  & 4  & MO   & 7  & PM    & 8  & MSFT  & 5  \\
MSFT & 6  & QCOM & 6  & TXN  & 4  & JPM  & 6  & ORCL  & 7  & MA    & 5  \\
INTC & 6  & C    & 6  & HPQ  & 3  & COP  & 6  & PG    & 7  & BABA  & 5  \\
WMT  & 6  & PG   & 6  & ORCL & 3  & T    & 6  & PEP   & 6  & FB    & 4  \\
GTE  & 5  & DELL & 5  & KO   & 2  & INTC & 6  & MSFT  & 6  & BAC   & 4  \\
MO   & 5  & ORCL & 4  & SUNW & 1  & AAPL & 6  & C     & 5  & INTC  & 4  \\
JNJ  & 4  & WMT  & 4  & LU   & 1  & BAC  & 5  & WFC   & 5  & GE    & 3  \\
PFE  & 4  & EMC  & 2  & EMC  & 0  & MT   & 4  & AMZN  & 5  & HD    & 3  \\
KO   & 2  & AOL  & 2  & NT   & 0  & AIG  & 4  & GILD  & 5  & AMZN  & 2  \\ \hline
\end{tabular}}
\caption{Outdegrees (Out) ranked for each sub-graph. Outdegree is defined as the number of edges going out of a specific node.}
\label{outdegree}
\end{table}

>>>>

A simple way to represent the DIG $G$ of a dynamical system is via the adjacency matrix $\textbf{DIG}=[d_{i,j}]_{m\times m}$ that is defined by
\begin{align}
    d_{j,i} = \left\{
\begin{array}{ll}
      1 & \text{if}\  I(R_i\rightarrow R_j||\mathcal{R}_{-\{i,j\}})>0,\\
      0 & \text{otherwise}. \\
\end{array} 
\right. 
\end{align}
Given a DIG $G=(\mathcal{V},\mathcal{E})$, we define the parent set of node $R_j$ denoted by $\mathcal{PA}_j\subset \mathcal{V}$ to be the set of all times series that have direct influences on $R_j$, i.e., $\mathcal{PA}_j:=\{R_k: d_{j,k}=1\}$. Similarly, the children set of node $R_j$ is given by $\mathcal{CH}_j:=\{R_k: d_{k,j}=1\}$. 
Next example demonstrates the DIG of a simple linear system.
\begin{example}\label{r1}
Consider a network of three times series $\{X,Y,Z\}$ with the following linear dynamic,
\begin{small}
\begin{equation}\label{model1}
\begin{pmatrix}
X_t \\
Y_t\\
Z_t
\end{pmatrix}=\begin{pmatrix}
0.5 & 0& 0\\
0.4 & 0.5 & 0\\
0 & -0.2 & 0
\end{pmatrix}\begin{pmatrix}
X_{t-1} \\
Y_{t-1}\\
Z_{t-1}
\end{pmatrix}+\begin{pmatrix}
N_{X_t} \\
N_{Y_t}\\
N_{Z_t}
\end{pmatrix},
\end{equation}
\end{small}
where $N_X$, $N_Y$, and $N_Z$ are three independent stationary Gaussian processes with zero mean and a diagonal covariance matrix (1, 0.9, 1). 
Since the dynamic is linear and the exogenous noises are Gaussian, we can compute the DIs using the following expression\footnote{Equation \eqref{simueq} does not hold in general setting.}\citet{acc2014}.
\begin{equation}\label{simueq}
I(Z\rightarrow Y||X)=\frac{1}{2T}\sum_{t=1}^{T}\log\frac{|\Sigma_{Y_{t-1},Y_{t},X_{t-1}}||\Sigma_{Z_{t-1},Y_{t-1},X_{t-1}}|}{|\Sigma_{Y_{t-1},X_{t-1}}||\Sigma_{Z_{t-1},Y_{t-1},Y_{t},X_{t-1}}|},
\end{equation}
where $|\Sigma_{Y_{t-1},Y_{t},X_{t-1}}|$ denotes the determinant of the covariance matrix of $\{Y_{t-1},Y_{t},X_{t-1}\}$. Using \eqref{simueq}, we computed the DIs of this system,
\begin{figure}
\hspace{4cm}
\xygraph{ !{<0cm,0cm>;<1.9cm,0cm>:<0cm,1.7cm>::} 
!{(-.7,1) }*+{X}="x"
!{(.4,1.6) }*+{Y}="y"
!{(1.5,1)}*+{Z}="z"
%"x":@(ld,lu)"x"
%"y":@(lu,ru)"y"
"x":"y"
"y":"z"
}
   \mycaption{DIG of the system in \eqref{model1}}{}
\label{fig:example_dig}
\end{figure}
\begin{small}
\begin{align*}
&I(Y\rightarrow X||Z)=0,\ \ I(Z\rightarrow X||Y)=0,\ \ I(Z\rightarrow Y||X)=0,\ \ I(Z\rightarrow Z||X,Y)=0,\\
&I(X\rightarrow Z||Y)=0,\ \ \ \ I(X\rightarrow Y||Z)\approx 0.1, \ \ \ I(Y\rightarrow Z||X)\approx 0.03.
\end{align*}
\end{small}
Figure \ref{fig:example_dig} illustrates the DIG of this system. In this example, $\mathcal{PA}_Z=\{Y\}$ and $\mathcal{CH}_Z=\{\}$.
\end{example}

@@

In this setting, the results of Lemma \ref{lemma:nonlinear} implies that the following time series can be substituted in the conditioning of the DI. 
\begin{align}
    Q_t = \sum_{k=1}^K w_{j,k} h_k(\mathcal{X}_{-\{i\},t-1}).
\end{align}
However, in this formulation, the weights $\{w_{,k}\}$ are unknown. 
An approach to obtain the weights is a non-linear filtering technique known as Koopman-based lifting \citet{koopman1931hamiltonian}. 
This technique takes observational data and a set of library functions as inputs and obtains the unknown coefficients $\{w_{,k}\}$.
The main steps of this technique are; transforming the data (lifting the data),  applying a linear identification on the lifted data, and finally applying another transformation to bring down the results into the original vector field.  Figure \ref{fig:koopman} illustrates the main steps. For more details see Appendix and \citet{mauroy2019koopman}. 
\begin{figure}
\centering
\includegraphics[scale=.4]{koopman.pdf}
\mycaption{Koopman lifting technique compared to classical non-linear identification}{}
\label{fig:koopman}
\end{figure}

@@

 \begin{algorithm}[t]
 \textbf{Input:} Observational data of $m$ time series up to time $T$, $\mathcal{X}^T$, Threshold $\alpha>0$\;
 \textbf{Output:} Adjacency matrix of $\textbf{DIG}=[d_{i,j}]$\;
 \For{ $i,j=1,...,m$}{
  Train an RNN $R_j(\cdot;\Theta^*)$ that maps $\mathcal{X}_{-\{i\}}^{t-1}$ to $X_{j,t}$\; 
  Define $Q_{t-1}=R_{j}(\mathcal{X}_{-\{i\}}^{t-1};\Theta^*)$\;
  \eIf{$I(X_{i}\rightarrow X_j || Q) > \alpha$}{
   $d_{j,i}=1$
   }{
   $d_{j,i}=0$
  }
  }
 \mycaption{Infer-DIG}{}
 \label{alg}
\end{algorithm}
 Given the aforementioned result, we train an RNN using the observational data to estimate the time series $Q$ defined in Lemma \ref{lemma:nonlinear}.
 More precisely, our RNN maps $\mathcal{X}_{-\{i\}}^{t-1}$ as the inputs to $X_{j,t}$ as the output. 
 Let $R_j(\mathcal{X}_{-\{i\}}^{t-1};\Theta^*)$ denotes the trained RNN with parameters $\Theta^*$. 
 In this case, the time series $Q$ can be written as  $Q_{t-1}=R_{j}(\mathcal{X}_{-\{i\}}^{t-1};\Theta^*)$.
 Finally, we use \eqref{eq:non-q} to detect whether $X_i$ has influence on $X_j$ or not. 
 Algorithm Infer-DIG in \ref{alg} summarizes the steps of our RNN method.

@@

To reflect an important property of the market that some firms are more connected than others in our experiment, we divided the $m$ time series into two parts. 
First part ($1\leq i\leq s$) indicates assets with high degrees of connectedness and the second part ($1+s\leq i\leq m$) are the ones with low degrees of connectedness.
Parameter $1<s<m$ denotes the numbers of assets with high degrees of connectedness.
Afterward, for every entry $(i,j)$ of $\textbf{A}$, we independently generated a random number $x\sim U(-0.9, 0.9)$ and decided on value $a_{i,j}$ as follows,
\begin{align}\label{eq:rules}
    a_{i,j}=\left\{
\begin{array}{ll}
      x 1_{|x| > \underline{\epsilon} },  & \text{if}\ \ 1\leq i\leq s, 1\leq j\leq s, \\
      x 1_{|x| > \overline{\epsilon} },  & \text{if}\ \ 1+s\leq i\leq m, 1\leq j\leq m, \\
      0,  & \text{if}\ \ 1\leq i\leq s, 1+s\leq j\leq m, \\
\end{array} 
\right.
\end{align}
where $1_{a>b}$ denotes the indicator function which is equal to 1 when $a>b$ and $0$ otherwise and $\underline{\epsilon}$ and $\bar{\epsilon}$ are thresholds to define non-zero entries in the upper-left and the lower part of $\textbf{A}$, respectively.
Figure \ref{fig:matrix} illustrates the structure of the resulting $\textbf{A}$.
We select these thresholds such that $\underline{\epsilon}<\bar{\epsilon}$. 
This ensures that the upper-left of $\textbf{A}$ is denser than its lower part or equivalently, assets with indices $\{1,...,s\}$ are more connected than the ones with indices $\{1+s,...,m\}$.
In our experiment, we select $(s,m)=(85,100)$ and $(\underline{\epsilon},\bar{\epsilon})=(0.4,0.7)$. 
%further results are robust to changes of parameters.
\begin{figure}
    \centering
    \includegraphics[scale=.2]{fig_matrix.pdf}
    \mycaption{Structure of matrix $\textbf{A}$ in \eqref{eq:ex_lin} that is build using \eqref{eq:rules}.}{}
    \label{fig:matrix}
\end{figure}
Finally, to guarantee the stability of the time series, we rescale\footnote{Formally, we use $\textbf{A}/(\rho(\textbf{A}) + \epsilon)$, where $0<\epsilon$.} $\textbf{A}$ such that its spectral radius is strictly less than one, i.e.,  $\rho(\textbf{A})< 1$. 
Once the matrix $\textbf{A}$ is defined, we simulate the time series using \eqref{eq:ex_lin} for a period of $T = 30000$ and use the resulting data for our estimations.

@@

\begin{figure*}
        \centering
        \begin{subfigure}[b]{0.48\textwidth}
            \centering
            \includegraphics[width=\textwidth]{Linear_Performance_True parents.jpg}
        \end{subfigure}
        \quad
        \begin{subfigure}[b]{0.48\textwidth}  
            \centering 
            \includegraphics[width=\textwidth]{Linear_Performance_Most correlated assets.jpg}
        \end{subfigure}
        \vskip\baselineskip
        \begin{subfigure}[b]{0.48\textwidth}   
            \centering 
            \includegraphics[width=\textwidth]{Linear_Performance_Ideal Portfolio.jpg}
        \end{subfigure}
                  \quad
        \begin{subfigure}[b]{0.48\textwidth}   
            \centering 
            \includegraphics[width=\textwidth]{Linear_Performance_RNN.jpg}
        \end{subfigure}
        \mycaption{Precision and recall curves in the linear framework.}{Precision and recall curves for the \textit{True parents}, \textit{Most correlated}, \textit{Ideal portfolio}, and the \textit{RNN}, respectively.} 
        \label{perflin}
    \end{figure*}

@@

\begin{figure}
\centering
\includegraphics[width=\textwidth]{precrecall_15assets.jpg}
\mycaption{Precision-Recall curves for the quadratic model.}{}
\label{fig:perfnonlin}
\end{figure}

@@

\end{tabular}
\mycaption{Degree of Granger Causality (DGC) for each sub-graph.}{DGC is defined as the fraction of relationships in the network among all potential relationships.}
\label{GrangerCausality}
\end{table}

\begin{figure*}
        \centering
        \begin{subfigure}[b]{0.6\textwidth}
            \centering
            \includegraphics[width=\textwidth]{net1994.JPG}
        \end{subfigure}
        \vskip\baselineskip
        \begin{subfigure}[b]{0.6\textwidth}   
            \centering 
            \includegraphics[width=\textwidth]{net1999.JPG}
        \end{subfigure}
        \mycaption{Empirical DIG for the periods 1990-1994 and 1995-1999.}{Empirical DIG for the periods 1990-1994 (top) and 1995-1999 (bottom). Interactive graphs can be found at https://marcaureledivernois.github.io/firm-network/} 
        \label{empdig1}
    \end{figure*}

\begin{figure*}[]
        \centering
        \begin{subfigure}[b]{0.6\textwidth}
            \centering
            \includegraphics[width=\textwidth]{net2004.JPG}
        \end{subfigure}
        \vskip\baselineskip
        \begin{subfigure}[b]{0.6\textwidth}   
            \centering 
            \includegraphics[width=\textwidth]{net2009.JPG}
        \end{subfigure}
        \mycaption{Empirical DIG for the periods 2000-2004 and 2005-2009.}{Empirical DIG for the periods 2000-2004 (top) and 2005-2009 (bottom). Interactive graphs can be found at https://marcaureledivernois.github.io/firm-network/} 
        \label{empdig2}
    \end{figure*}

\begin{figure*}
        \centering
        \begin{subfigure}[b]{0.6\textwidth}
            \centering
            \includegraphics[width=\textwidth]{net2014.JPG}
        \end{subfigure}
        \vskip\baselineskip
        \begin{subfigure}[b]{0.6\textwidth}   
            \centering 
            \includegraphics[width=\textwidth]{net2019.JPG}
        \end{subfigure}
        \mycaption{Empirical DIG for the periods 2010-2014 and 2015-2019.}{Empirical DIG for the periods 2010-2014 (top) and 2015-2019 (bottom). Interactive graphs can be found at https://marcaureledivernois.github.io/firm-network/} 
        \label{empdig3}
    \end{figure*}

\begin{table}[]
\resizebox{\textwidth}{!}{
\begin{tabular}{|ll|ll|ll|ll|ll|ll|}
\hline
\multicolumn{2}{|c|}{1990-1994} &
  \multicolumn{2}{c|}{1995-1999} &
  \multicolumn{2}{c|}{2000-2004} &
  \multicolumn{2}{c|}{2005-2009} &
  \multicolumn{2}{c|}{2010-2014} &
  \multicolumn{2}{c|}{2015-2019} \\ \hline
Ticker &
  Out &
  Ticker &
  Out &
  Ticker &
  Out &
  Ticker &
  Out &
  Ticker &
  Out &
  Ticker &
  Out \\ \hline
SBC  & 13 & JNJ  & 12 & XOM  & 12 & PEP  & 15 & SPY   & 17 & SPY   & 14 \\
CHV  & 11 & HWP  & 12 & JNJ  & 10 & WFC  & 13 & T     & 15 & DIS   & 12 \\
XON  & 10 & INTC & 12 & MSFT & 9  & CSCO & 12 & JNJ   & 15 & BRK   & 12 \\
PG   & 10 & BAC  & 12 & DELL & 9  & WMT  & 11 & CVX   & 13 & PFE   & 11 \\
GE   & 10 & PFE  & 11 & WMT  & 9  & IBM  & 11 & AAPL  & 12 & UNH   & 11 \\
AN   & 9  & IBM  & 11 & C    & 9  & PG   & 11 & INTC  & 12 & JPM   & 11 \\
BEL  & 9  & MSFT & 11 & HD   & 8  & CVX  & 11 & CSCO  & 12 & AAPL  & 10 \\
MRK  & 8  & SBC  & 11 & JPM  & 8  & HPQ  & 10 & GE    & 12 & GOOGL & 10 \\
IBM  & 8  & GE   & 10 & PFE  & 8  & VZ   & 10 & IBM   & 11 & WMT   & 9  \\
BMY  & 8  & MRK  & 10 & PG   & 7  & GE   & 9  & GOOGL & 11 & CSCO  & 9  \\
ABT  & 7  & LMG  & 9  & INTC & 7  & UBS  & 9  & XOM   & 11 & VZ    & 9  \\
AHP  & 7  & MO   & 9  & BAC  & 7  & PFE  & 9  & JPM   & 10 & BA    & 9  \\
T    & 7  & NT   & 9  & BMY  & 6  & C    & 9  & KO    & 10 & CVX   & 8  \\
BLS  & 7  & XOM  & 9  & SBC  & 6  & SLB  & 9  & MRK   & 10 & WFC   & 8  \\
AIG  & 7  & KO   & 9  & IBM  & 5  & MSFT & 9  & BRK   & 10 & V     & 8  \\
F    & 7  & HD   & 8  & TWX  & 5  & ORCL & 9  & SLB   & 10 & PG    & 8  \\
HWP  & 7  & BEL  & 8  & AIG  & 5  & MRK  & 8  & WMT   & 10 & T     & 7  \\
MOT  & 7  & BMY  & 8  & CSCO & 4  & KO   & 8  & VZ    & 9  & JNJ   & 7  \\
DD   & 6  & SUNW & 8  & GE   & 4  & GOOG & 7  & DIS   & 9  & MRK   & 7  \\
DIS  & 6  & AIG  & 7  & VZ   & 4  & XOM  & 7  & PFE   & 9  & KO    & 6  \\
MOB  & 6  & WCOM & 7  & MRK  & 4  & JNJ  & 7  & BAC   & 8  & XOM   & 5  \\
PEP  & 6  & CSCO & 6  & MOT  & 4  & MO   & 7  & PM    & 8  & MSFT  & 5  \\
MSFT & 6  & QCOM & 6  & TXN  & 4  & JPM  & 6  & ORCL  & 7  & MA    & 5  \\
INTC & 6  & C    & 6  & HPQ  & 3  & COP  & 6  & PG    & 7  & BABA  & 5  \\
WMT  & 6  & PG   & 6  & ORCL & 3  & T    & 6  & PEP   & 6  & FB    & 4  \\
GTE  & 5  & DELL & 5  & KO   & 2  & INTC & 6  & MSFT  & 6  & BAC   & 4  \\
MO   & 5  & ORCL & 4  & SUNW & 1  & AAPL & 6  & C     & 5  & INTC  & 4  \\
JNJ  & 4  & WMT  & 4  & LU   & 1  & BAC  & 5  & WFC   & 5  & GE    & 3  \\
PFE  & 4  & EMC  & 2  & EMC  & 0  & MT   & 4  & AMZN  & 5  & HD    & 3  \\
KO   & 2  & AOL  & 2  & NT   & 0  & AIG  & 4  & GILD  & 5  & AMZN  & 2  \\ \hline
\end{tabular}}
\mycaption{Outdegrees ranked for each sub-graph.}{Outdegree (Out) is defined as the number of edges going out of a specific node.}
\label{outdegree}
\end{table}
